%███
% need specifically 1 new line
%███

\subsubsection{[Mathematical Framework]}%███

\noindent \hypertarget{def-Reference-frame}{\textbf{Reference frame:}} 
An abstract coordinate system taken to be at rest consisting of three spatial and one time axis. The origin of its axis, its orientation, and its scale are specified by a set of points in space. The purpose of it is to provide a standardised means of defining the position of objects within that frame at any instant of time.

\noindent \hypertarget{def-Inertial-reference-frame}{\textbf{Inertial reference frame:}}
A reference frame that is not undergoing any acceleration. An observer's reference frame is inertial if they do not feel a force being acted on then.

\noindent \hypertarget{def-proper-frame}{\textbf{Proper/Rest frame:}} 
The Proper/Rest frame of an object, is the reference frame of the object itself.

\noindent \hypertarget{def-Primed-Frame}{\textbf{Primed frame:}}
A reference frame that is moving relative to the current frame.

\noindent \hypertarget{def-frame-velocity}{\textbf{frame velocity:}} 
The velocity of a reference frame relative to the current reference frame.

\noindent \hypertarget{def-transform}{\textbf{Frame transform:}} 
The changing of coordinates and other quantities in a reference frame into their corresponding values in another reference frame.

\noindent \hypertarget{def-galilean-transform}{\textbf{Galilean/Classical frame transform:}}
Transformation of coordinates and physical quantities according to Newtonian physics.

\noindent \hypertarget{def-lorentz-transform}{\textbf{Relativistic frame transform:}} 
The changing of the spatial coordinates, time coordinate, and other physical quantities into their corresponding values in a different inertial reference frame using equations from special relativity.

\noindent \hypertarget{def-observer}{\textbf{Observer:}}
An entity/thing that has an associated a frame of reference/system of coordinates in which to measure the position, orientation, and other properties of objects with respect to.

\noindent \hypertarget{def-event}{\textbf{Event:}}
An occurrence that can be that can be specified by a unique combination of the three spatial and one time coordinates. These four coordinates, together, form a point in spacetime.

\noindent \hypertarget{def-simultaneity}{\textbf{Simultaneity:}}
Within a reference frame, two or more events are simultaneous if they occur at the same time in it. Classically if any two events are simultaneous in one reference frame, they are also simultaneous in any other reference frame. In special relativity, this is not true, and the order of events can depend on the frame of reference.

\noindent \hypertarget{def-retarded-position}{\textbf{Retarded P
position:}}
The previous position of a source of a field that an observer sees it at at, due to the time delay between when a source emits a field and when that field is detected by the observer


\subsubsection{[The Mechanics]}%██████████████████

\noindent \hypertarget{def-aether}{\textbf{Aether:}}
A proposed medium that filled the vacuum of space that light propagated through.

\noindent \hypertarget{def-vacuum}{\textbf{Vacuum:}}
Empty space with no matter and negligible amount of effects from fields.

\noindent \hypertarget{def-length-contraction}{\textbf{Lorentz length contraction:}}
The shortening of an object along the direction of its motion relative to an observer (relative to the object at rest).

\noindent \hypertarget{def-time-dilation}{\textbf{Time dilation:}}
The slowing of the passing of time for objects in motion relative an observer, compared to the passing of time for the observer.

\noindent \hypertarget{def-doppler-effect}{\textbf{Doppler effect:}}
The change of a wave's frequency due to the relative motion of its source to an observer. This is due to the bunching up of the wave in the direction of movement of the source and the stretching of the wave in the opposite direction, as well as the dilation of time between two parts of the emitted wave.

\noindent \hypertarget{def-aberration}{\textbf{Aberration of light:}}
The changing of the direction of the propagation of light when moving into another reference frame.

\noindent \hypertarget{def-relativistic-beaming}{\textbf{Relativistic beaming:}}
The accumulation of the Doppler effect and aberration of light, and how it effects the amount of light and its frequency emitted at difference angles from a moving source. This effect can be extended to any wave or field being emitted at the speed of light from a moving source.

\noindent \hypertarget{def-retarded-field}{\textbf{Retarded field:}}
A moving source's field, where at each point has been propagated at the speed of light from the retarded position of the source...

\noindent \hypertarget{def-field}{\textbf{Field:}}


\subsubsection{[Defs for later]}%██████████████████

\noindent \hypertarget{def-lorentz-invariant}{\textbf{Invariant:}}
...
